---
title: "byte4"
author: "Lina Osorio"
date: "April 16, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This document explores the interaction of end users with the Wikipedia interface. Specifically, the most popular principal articles that people requests, also the articles that end users request before and after getting into a particular article. The information used was the Wikipedia Clickstream February 2015 dataset <https://figshare.com/articles/Wikipedia_Clickstream/1305770>. 

The dataset has the following four variables: 
**Source** is the result of mapping the refereed URL to a set of values that correspond to the internal traffic of Wikipedia.  
**Target** is the unique MediaWiki page ID of every article that a client requested.  
**Type** is a variable that can take three possible values. "link" which referes that both articles were refered within Wikipedia. "Redlink" which refers to a requests that does not link to a enwiki.page table. "Other" refers to an article that does not link to the request.  
**Occurrences** shows the number of occurrences of the (refer, resource) pair.  

**Note**: the raw data only includes pairs with 10 or more occurrences.

# Cleaning and Exploring data

I filtered the variable type equal to "link" gettin the source and target pairs that represent the internal Wikipedia traffic.

```{r libraries, include=FALSE}
# install.packages("devtools")
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})

#install.packages(c("igraph", "ggraph"))
#devtools ::install_github("tidyverse/ggplot2")
#devtools::install_github("stan-dev/rstan", ref = "develop", subdir = "rstan/rstan")
library(readr)
library(data.table)
library(plyr)
library(dplyr)
library(tidyr)
library(magrittr)
library(igraph)
library(ggraph)
library(ggplot2)
library(pander)
library(gridExtra)
```

```{r getting data, include=FALSE}

## titles
X <- read.csv(url("https://s3-eu-west-1.amazonaws.com/pfigshare-u-files/5036383/2015_02_en_clickstream.tsv.gz"))
#fd <- "C:/Users/linos/Desktop/rbyte4"
#setwd(fd)

only_link <- read.table("only_link.tsv")
```

```{r additional datasets, include=FALSE}
sel <- c("target", "occurrences")

tar_occ <- only_link[sel]

tar_occ_agg <- aggregate(tar_occ$occurrences, by=list(target=tar_occ$target), FUN=sum)

tar_occ_agg_top10 <- tar_occ_agg[order(desc(tar_occ_agg$x)),]

sel2 <- c("source", "occurrences")

sour_occ <- only_link[sel2]

sour_occ_agg <- aggregate(sour_occ$occurrences, by=list(source=sour_occ$source), FUN=sum)

sour_occ_agg_top10 <- sour_occ_agg[order(desc(sour_occ_agg$x)),]
```

The next table shows the top 10 articles that were more requested during the selected time period. 
```{r table1, echo=FALSE}
top10_occ <- head(tar_occ_agg_top10,10)

names(top10_occ) <- c("Target", "Occurrences")

pander(top10_occ, type = 'grid')
```
Contrary to the previous table, the next one shows the main sources. For example, one of the more frequently requested source article is Meghan_Markle, and Price_Harry one of the main targets. It means that most of users that look for Meghan_Markle's article request a target article after, while the users that reach Prince_Harry article do not request another one after reading it.

```{r table2, echo=FALSE}
top10_sour <- head(sour_occ_agg_top10,10)

names(top10_sour) <- c("Source", "Occurrences")

pander(top10_sour, type = 'grid')
```

```{r include=FALSE}
g <- graph_from_data_frame(only_link, directed = TRUE)
```


## Visualization

The next two network graphs show the interaction around two principal articles. Communism and Capitalism.

### Capitalism and Communism
```{r capitalism, include=FALSE, warning=FALSE}
## working with graphs capitalism
sg <- make_ego_graph(g, order = 1, mode = "out", V(g)["Capitalism"])[[1]]

# Number of neighbors:
V(sg)$edges <- degree(sg)

# Labels where the spaces aren't underscores:
V(sg)$label <- gsub("_", " ", V(sg)$name, fixed = TRUE)

ssg <- induced_subgraph(sg, V(sg)[edges > 45])

```

```{r, echo=FALSE, warning=FALSE}
## visualization

set.seed(10) # for reproducibility
ggraph(ssg, layout = "dh") +
geom_edge_diagonal(aes(alpha = log10(occurrences))) +
scale_edge_alpha_continuous("Clicks", labels = function(x) { return(ceiling(10 ^ x)) }) +
geom_node_label(aes(label = label, size = edges)) +
scale_size_continuous(guide = FALSE) +

theme_graph() +
theme(legend.position = "bottom")

ggsave(capitalism[4], plot = last_plot(), device = jpeg,
  scale = 1, width = NA, height = NA,
  dpi = 300, limitsize = TRUE)
```

```{r communism, include=FALSE, warning=FALSE}
## working with graphs capitalism
sg1 <- make_ego_graph(g, order = 1, mode = "out", V(g)["Communism"])[[1]]

# Number of neighbors:
V(sg1)$edges <- degree(sg1)

# Labels where the spaces aren't underscores:
V(sg1)$label <- gsub("_", " ", V(sg1)$name, fixed = TRUE)

ssg1 <- induced_subgraph(sg1, V(sg1)[edges > 55])

```

```{r echo=FALSE, warning=FALSE}
## visualization

set.seed(1000) # for reproducibility
ggraph(ssg1, layout = "dh") +
geom_edge_diagonal(aes(alpha = log10(occurrences))) +
scale_edge_alpha_continuous("Clicks", labels = function(x) { return(ceiling(10 ^ x)) }) +
geom_node_label(aes(label = label, size = edges)) +
scale_size_continuous(guide = FALSE) +

theme_graph() +
theme(legend.position = "bottom")
```

These two networks show that people that requested the article Communism frequently go through the article Capitalism.  It might mean that  some of the users that look for information to contrast opossite topics. This analysis does not allow reliable conclusions about users reasoning and motivations to look for those topics. Further study is needed to get stronger evidence. For example, looking for a broader group of paired themes; making a network analysis to calculate closeness between nodes.

Finally, I used the code used for the net_neutrality analysis to build the network graphs in R. <https://blog.wikimedia.org/2018/01/18/on-that-net-neutrality-clickstream-diagram/>
